Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-07 BN_discretizer_paper.tex
delete a reductant "the"
png figures to eps figures
change figure files

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx} % Allows including images
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\setcitestyle{aysep={ }} %Author-Year SEParator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

Finally, we can combine the our new discretization method with the K2 structure learning alorithm \citep{K2}. We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete. Each time an edge is added in the K2 algorithm procedure, we rediscretize the continuous variables based on the updated Bayesian network and store the result for the next K2 algorithm iteration. By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.

@@

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=6cm]{graph1.png}
% figure caption is below the figure
\caption{Factorization of $P(D \mid M)$}
\label{fig:1}       % Give a unique label
\end{figure}

@@

With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently. For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
\begin{equation}
\begin{aligned}
 \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right. \right.\\ 
& \left.  \log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
&  \left. \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
\end{aligned}
\end{equation}
In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket. Therefore, in this case, child variables are more determinative than parent variables even though the numbers of child variables and parent variables are equal. However, if $C_2$ has the other parent variable $S_2$, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$. These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.

\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=9cm]{graph2.png}
% figure caption is below the figure
\caption{Two example networks}
\label{fig:2}       % Give a unique label
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx} % Allows including images
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year SEParator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

Finally, we can combine our new discretization method with the K2 structure learning alorithm \citep{K2}. We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete. Each time an edge is added in the K2 algorithm procedure, we rediscretize the continuous variables based on the updated Bayesian network and store the result for the next K2 algorithm iteration. By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.

@@

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph1}
    \end{tabular}
  \caption{Factorization of $P(D \mid M)$}
\end{figure}

@@

With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently. For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
\begin{equation}
\begin{aligned}
 \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right. \right.\\ 
& \left.  \log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
&  \left. \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
\end{aligned}
\end{equation}

In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket. Therefore, in this case, child variables are more determinative than parent variables even though the numbers of child variables and parent variables are equal. However, if $C_2$ has the other parent variable $S_2$, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$. These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph2_left} 
      \end{tabular}
     \hspace{5em}
      \begin{tabular}{cc}
      \input{graph2_right} 
    \end{tabular}
  \caption{Two example networks}
\end{figure}
